Understanding the impacts of video-guided activities on parent-child interaction

### 2019-09-17 paper/manuscript.Rmd
tweaked combined plots

```{r hiddenfigs, include=F}
e1ttr <- ggplot(e1_lex, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .7)) +
  geom_point(data=e1ld, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Type/Token Ratio (TTR)") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle("Experiment 1")

e1mtld <- ggplot(e1_mtld, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e1ld, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("MTLD") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none") + ggtitle(" ")

e1tokens <- ggplot(e1_tok, aes(x=Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e1ld, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Number of Word Tokens") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle(" ")

@@

```{r fig-lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6.5, fig.height=5.5, fig.cap = "\\label{fig:lexdiv} Mean lexical diversity scores (left: Type/Token ratio, middle: MTLD) and mean number of tokens used by condition in Experiment 1 (top) and Experiment 2 (bottom). Error bars show bootstrapped 95\\% confidence intervals (CIs), and gray dots indicate values for each participant."}

@@

e2ttr <- ggplot(ttr2, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + # labels=addline_format(c("Science Video", "Activity Video"))
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2data, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Type/Token Ratio (TTR)") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle("Experiment 2")

@@

e2mtld <- ggplot(mtld2, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2data, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("MTLD") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle(" ")

@@

e2tokens <- ggplot(e2tok, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2data, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Number of Word Tokens") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle(" ")

@@

We fit a mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR. 
This lme4 model included random intercepts per video. 
There were significantly more bids for JA in the Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the Control condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 95% CI=[`r e1bids['95pLB']`,`r e1bids['95pUB']`]).

@@

e1bids <- ggplot(ms_bids1, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e1ja, aes(x=Condition, y=bids_tot), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Mean Bids for Joint Attention") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none") + ggtitle("Experiment 1")
 # theme(plot.title = element_text(size = 13, face = "bold"))
# total joint attention episodes
ms_tja1 <- e1ja %>% group_by(Condition) %>%
  tidyboot_mean(total_ja)

e1tja <- ggplot(ms_tja1, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e1ja, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Mean Episodes of Joint Attention") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none") + ggtitle(" ")

@@

e2_bids <- e2ja %>% group_by(Condition) %>%
  tidyboot_mean(bids)
e2bids <- ggplot(e2_bids, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2ja, aes(x=Condition, y=bids), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Bids for Joint Attention") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none") + ggtitle("Experiment 2")

# total JA episodes
e2_tja <- e2ja %>% group_by(Condition) %>%
  tidyboot_mean(total_ja) 
e2tja <- ggplot(e2_tja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2ja, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Episodes of Joint Attention") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none") + ggtitle(" ")

e2tja_age = ggplot(e2ja, aes(x = Age, y = total_ja, group=Condition, colour = Condition)) +
  geom_point(alpha=.7) + geom_smooth(method='lm') + 
  xlab("Age (years)") + ylab("Total Episodes of Joint Attention") +
  langcog::scale_colour_solarized() +
  ggthemes::theme_few() + ggtitle(" ")

# multiplot(e1bids, e1tja, cols=2) # old Exp1
# multiplot(e2bids, e2tja_age, cols=5, layout=matrix(c(1,1,2,2,2), nrow=1))
multiplot(e1bids, e1tja, e2bids, e2tja_age, 
          cols=6, layout=matrix(c(1,1,1,2,2,2, 3,3,4,4,4,4), nrow=2, byrow=T)) 
```

>>>>

```{r e1ld-figs, include=F}
small_text = theme(
  plot.title = element_text(size = 12, face="bold"),
  axis.title.x = element_text(size = 10),
  axis.text.x = element_text(size = 8),
  axis.title.y = element_text(size = 10),
  axis.text.y = element_text(size = 8))

e1ttr <- ggplot(e1_lex, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .7)) +
  geom_point(data=e1ld, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Type/Token Ratio (TTR)") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle("Experiment 1") + small_text
# want carriage return in Condition labels..

e1mtld <- ggplot(e1_mtld, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e1ld, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("MTLD") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none") + ggtitle(" ") + small_text

e1tokens <- ggplot(e1_tok, aes(x=Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e1ld, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Number of Word Tokens") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle(" ") + small_text

@@

```{r fig-lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6.5, fig.height=5.5, fig.cap = "\\label{fig:lexdiv} Mean lexical diversity scores (left: Type/Token ratio, middle: MTLD) and mean number of tokens used by condition (right) in Experiment 1 (top) and Experiment 2 (bottom). Error bars show bootstrapped 95\\% confidence intervals (CIs), and gray dots indicate values for each participant."}

@@

e2ttr <- ggplot(ttr2, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + # labels=addline_format(c("Science Video", "Activity Video"))
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2data, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Type/Token Ratio (TTR)") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle("Experiment 2") + small_text

@@

e2mtld <- ggplot(mtld2, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2data, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("MTLD") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle(" ") + small_text

@@

e2tokens <- ggplot(e2tok, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2data, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Number of Word Tokens") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle(" ") + small_text

@@

We fit a mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR. 
This model included random intercepts per video. 
There were significantly more bids for JA in the Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the Control condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 95% CI=[`r e1bids['95pLB']`,`r e1bids['95pUB']`]).

@@

e1bids <- ggplot(ms_bids1, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e1ja, aes(x=Condition, y=bids_tot), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Mean Bids for Joint Attention") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none") + ggtitle("Experiment 1") + small_text

# total joint attention episodes
ms_tja1 <- e1ja %>% group_by(Condition) %>%
  tidyboot_mean(total_ja)

e1tja <- ggplot(ms_tja1, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e1ja, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Mean Episodes of Joint Attention") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none") + ggtitle(" ") + small_text

@@

library("scales")
#show_col(solarized_pal()(2)) # blue, red
sol_colors = solarized_pal()(2)

e2_bids <- e2ja %>% group_by(Condition) %>%
  tidyboot_mean(bids)
e2bids <- ggplot(e2_bids, aes(x = Condition, y = mean, fill = str_wrap(Condition, 8))) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  labs(fill="Condition") + 
  geom_point(data=e2ja, aes(x=Condition, y=bids), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Bids for Joint Attention") + 
  scale_fill_manual(values=sol_colors) + ggthemes::theme_few() + ggtitle("Experiment 2") + small_text +
  theme(legend.key.height=unit(1.2, "cm"), legend.text=element_text(size=9))

# total JA episodes (not currently graphed)
e2_tja <- e2ja %>% group_by(Condition) %>%
  tidyboot_mean(total_ja) 
e2tja <- ggplot(e2_tja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2ja, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Episodes of Joint Attention") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  ggtitle(" ") + small_text + theme(legend.position="none")

e2tja_age = ggplot(e2ja, aes(x = Age, y = total_ja, group=Condition, colour=Condition)) +
  geom_point(alpha=.8) + geom_smooth(method='lm') + scale_colour_manual(values=rev(sol_colors)) +
  xlab("Age (years)") + ylab("Total Episodes of Joint Attention") +
  ggthemes::theme_few() + ggtitle(" ") + small_text + theme(legend.position="none")

# multiplot(e1bids, e1tja, cols=2) # old Exp1
# multiplot(e2bids, e2tja_age, cols=5, layout=matrix(c(1,1,2,2,2), nrow=1))
multiplot(e1bids, e1tja, e2bids, e2tja_age, 
          cols=6, layout=matrix(c(1,1,1,2,2,2, 3,3,3,4,4,4), nrow=2, byrow=T)) 
```

### 2019-09-17 paper/manuscript.tex
tweaked combined plots

\caption{\label{fig:lexdiv} Mean lexical diversity scores (left: Type/Token ratio, middle: MTLD) and mean number of tokens used by condition in Experiment 1 (top) and Experiment 2 (bottom). Error bars show bootstrapped 95\% confidence intervals (CIs), and gray dots indicate values for each participant.}\label{fig:fig-lexdiv}
\end{figure}

@@

We fit a mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
This lme4 model included random intercepts per video.
There were significantly more bids for JA in the Video condition (mean: 6.30, sd: 2.76) than in the Control condition (mean: 3.73, sd: 2.74, \(\beta=3.40\), 95\% CI={[}1.03,5.73{]}).

>>>>

\caption{\label{fig:lexdiv} Mean lexical diversity scores (left: Type/Token ratio, middle: MTLD) and mean number of tokens used by condition (right) in Experiment 1 (top) and Experiment 2 (bottom). Error bars show bootstrapped 95\% confidence intervals (CIs), and gray dots indicate values for each participant.}\label{fig:fig-lexdiv}
\end{figure}

@@

We fit a mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
This model included random intercepts per video.
There were significantly more bids for JA in the Video condition (mean: 6.30, sd: 2.76) than in the Control condition (mean: 3.73, sd: 2.74, \(\beta=3.40\), 95\% CI={[}1.03,5.73{]}).
